---
title: "VWO Surveys NLP Analysis"
date: "3/12/2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<br />  

## Context

The anlytics team, in tandem with so and so and so and so, ran a series of surveys on the website from this date to this date. The surveys were targets to different pages, on different platforms, to different user types (subscriber v. non-subscriber). In total, 9 surveys were conducted and over 6,000 responses were collected. 
<br />   
<br />  

## Overview


When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
word_counts %>%
  arrange(desc(n)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>%
  group_by(segment) %>%    
  top_n(10) %>%
  ungroup %>%
  
  ggplot(aes(word, n)) +
  theme_light() +
  geom_col(aes(fill = segment), show.legend = F) +
  facet_wrap(~segment, ncol = 3, scales = "free") +                   # separate by segment
  labs(y = "# of times word appeared", x = "word") +
  coord_flip() +
  ggtitle("Top 10 Words by Survey, All Surveys") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))        # title formatting (center, bold)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
